### 2016-12-28 paper/paper.tex
typesetting tweaks

\newcommand{\acronym}[1]{\small{#1}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\Gaia}{\project{Gaia}}

\begin{document}

\section*{A photometric method for obtaining spectroscopic parameters of stars}

@@

This work has made use of data from the European Space Agency (ESA)
mission \Gaia\ (http://www.cosmos.esa.int/gaia), processed by the \Gaia
Data Processing and Analysis Consortium (\acronym{DPAC},
http://www.cosmos.esa.int/web/gaia/dpac/consortium). Funding for the
\acronym{DPAC} has been provided by national institutions, in particular the
institutions participating in the Gaia Multilateral Agreement.

>>>>

\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\Gaia}{\project{Gaia}}

\linespread{1.09}
\setlength{\parindent}{1.2\baselineskip}
\sloppy\sloppypar\raggedbottom\frenchspacing
\begin{document}

\section*{\raggedright%
A photometric method for obtaining spectroscopic parameters of stars}

@@

This work has made use of data from the European Space Agency (ESA)
mission \Gaia\ (http://www.cosmos.esa.int/gaia), processed by the \Gaia\ %
Data Processing and Analysis Consortium (\acronym{DPAC},
http://www.cosmos.esa.int/web/gaia/dpac/consortium). Funding for the
\acronym{DPAC} has been provided by national institutions, in particular the
institutions participating in the Gaia Multilateral Agreement.
